### 2020-05-15 draft_ABP.tex
Update draft_ABP.tex
Updates from Overleaf

{\Large \bf  Binary geometries: Associahedra, Cyclohedra and (Generalized) Permutahedra}

@@

In \cite{Arkani-Hamed:2019mrd} the study of stringy canonical forms and binary geometries with ``perfect'' $u$-equations, associated with the scattering of particles and strings was initiated. In this paper we continue the study of binary geometries and find two large classes of new examples.  The first class corresponds to degenerations of $A_n$ and $B_n$ (associahedra and cyclohedra respectively) which have perfect $u$-equations. The second class corresponds to a large subset of  generalized permutahedra which can be realised as degenerations of the permutahedron $P_n$ which are binary positive geometries despite not having perfect $u$-equations. Both these large classes of examples have stringy integrals which factorise at any finite $\alpha^{'}$  on all the massless poles.

@@

\newpage
\section{Introduction}

In \cite{Arkani-Hamed:2019mrd} the notion of {\it stringy canonical forms} were introduced as a general framework for generalizing tree-level string amplitudes, or integrals over the moduli space ${\cal M}_{0, n}$. Various nice properties of string amplitudes and their field-theory limits, such as factorizations for $\alpha' \to 0$ limit and finite $\alpha'$, channel duality and exponent softness, scattering equations, {\it etc.} all naturally extend to stringy canonical forms. To briefly summarize the idea, let's begin with the disk integral for open-string amplitudes with ordering $(1,2,\cdots, n)$:
\begin{equation}\label{stringint}
{\cal I}^{\rm open-string}_{1,2,\cdots,n} (\{s\}):=\int_{\mathcal M_{0,n}^+}
\frac{\mathrm d^{n}z}{\mathrm{SL}(2,\mathbb{R})} \prod_{i=1}^{n}\frac{1}{z_{i}-z_{i{+}1}}
\prod_{i<j}(z_j{-}z_i)^{\alpha' s_{ij}},
\end{equation}
where $\mathcal M_{0,n}^+$ is the positive part of moduli space for the ordering, and $\mathsf{PT}_n:=\frac{\mathrm d^{n}z}{\mathrm{SL}(2,\mathbb{R})} \prod_{i=1}^{n}\frac{1}{z_{i}-z_{i+1}}$ its canonical form~\cite{};  %each factor  $(z_j-z_i)$ in the Kobe-Nieson factor $\prod_{i<j}(z_j-z_i)^{\alpha' s_{ij}}$ is a nowhere vanishing function on $\mathcal M_{0,n}^+$.
With a positive parameterization $\{x_1,\dots,x_{n-3}\}$ of $\mathcal M_{0,n}^+$, 
this canonical form becomes $\prod_{i=1}^{n-3}\mathrm d \log x_i$, and the Koba-Nieson factor $\prod_{i<j}(z_j-z_i)^{\alpha' s_{i j}}$ becomes a product of powers of polynomials with 
non-negative coefficients~\cite{}: $\prod_i x_i^{\alpha' X_i} \prod_I p_I(x)^{-\alpha' c_I}$. Note that we have factored out $n{-}3$ monomials, $x_i$, and left with $n(n{-}3)/2-(n{-}3)$ positive polynomials $p_I(x)$, with exponents $X_i$'s and $c_I$'s given by linear combinations of the Mandelstam variables $s_{i,j}$.

\paragraph{Stringy canonical forms} Motivated by this rewriting of string integral~\eqref{stringint}, we define a general stringy integral as a $d$-dimensional integral~\cite{Arkani-Hamed:2019mrd}
\begin{equation}\label{stringycanonicalform}
	\mathcal I (\mathbf X,\{c\})=
	\int_{\mathbb R_+^d}\prod_{i=1}^d \frac{\mathrm d x_i}{x_i}x_i^{\alpha'X_i}
	\prod_{I=1}^m p_I(x)^{-\alpha' c_I},
\end{equation}
where we allow $m$ arbitrary Laurent polynomial with non-negative coefficients, $p_I(x)$, and without loss of generality we assume exponents $X_i>0$ and $c_I>0$~\footnote{These are ``positive'' stringy canonical forms, which are integrals over $\mathbb R_+^d$. We can also consider ``complex'' case with the integrand mod-squared and integrated over $\mathbb C^d$, which are generalizations of closed-string amplitudes~\cite{}.}.

Any integral of the form \eqref{stringycanonicalform} inherits various remarkable properties of string amplitudes \eqref{stringint}, which all depend on the existence of a polytope $\mathcal P:=\sum_I c_I N[p_I]$; here $N[p_I]$ is the Newton polytope of the polynomial $p_I$, and we take the (weighted) Minkowski sum~\cite{}. First of all, one can show that the integral \eqref{stringycanonicalform} is convergent if and only if $\mathbf X=(X_1,\dots,X_d)$ is in the interior of the polytope $\mathcal P$ (we assume that ${\cal P}$ is $d$ dimensional). The leading order of the integral in its $\alpha'$ expansion, dressed with $d^d \mathbf X$, is given by the canonical form of the polytope, ${\Omega}(\cal P)$, thus it can be viewed as $\alpha'$-deformation of $\Omega(\cal P)$ (hence the name ``stringy canonical form"). Generically the poles of $\Omega(\cal P)$ are given by equations of
facets for $\mathcal P$, which are also poles of the integral at finite $\alpha'$, and the residue on any such pole is given by a stringy canonical form defined for that facet (see~\cite{} for details).

For the string integral \eqref{stringint}, ${\cal P}$ is nothing but the ABHY associahedron~\cite{Arkani-Hamed:2017mur}, whose canonical form gives bi-adjoint $\phi^3$ amplitude as the $\alpha'\to 0$ limit of \eqref{stringint}~\cite{}. The poles are the planar variables $X_{i,j}$, on which \eqref{stringint} factorizes into lower-point integrals even for finite $\alpha'$. Moreover, the saddle point equations as $\alpha' \to \infty$ can be written as $X_i=\sum_I c_I \partial \log p_I/\partial \log x_i$ for $i=1,\cdots, d$; they provide a diffeomorphism from the integration domain to ${\cal P}$, thus $\Omega(\mathcal P)$ can be computed as a pushforward of $\prod_i d\log x_i$ via summing over the saddle points~\cite{Arkani-Hamed:2017tmz}. In particular, for the string integral \eqref{stringint}, the scattering equations provide a map from ${\cal M}_{0,n}^+$ to ABHY associahedron, and the pushforward is equivalent to the CHY formula for $\phi^3$ amplitude~\cite{}.

\paragraph{Configuration spaces} One way to describe the combinatorics of the polytope ${\cal P}$ is through the {\it configuration space}, {\it e.g.} as blow-up of $\mathbb R_+^D$ in the $\mathbf x$-space. However, it is usually difficult to use $\mathbf x$ for this, even for the string integrals \eqref{stringint}. For example, a facet usually corresponds to a complicated limit process with $x \to 0$ or $\infty$. As proposed in~\cite{}, an elegant way to realize ${\cal P}$ in configuration space is by introducing a set of constrained $u$ variables $\{u_\alpha\}$. The configuration space is the variety defined by a set of polynomial equations satisfied by $\{u_\alpha\}$ (or $u$ equations), and the polytope ${\cal P}$ can be realized combinatorially by $\{u_\alpha \geq 0\}$. 
%facet is simply given by an equation $u_A=0$. 
To define the $u$ variables, we first construct the so-called \textit{big polyhedron} in the space $\mathbf S:=(X_1,\dots,X_d,-c_1,\dots,-c_m) \in \mathbb R^{d{+}m}$.  %then $\{u_A\}$ 
%\[
%	\int_{\mathbb R_+^m}\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
%	\prod_{A}u_A^{\alpha' U_A}
%	=
%	\int_{\mathbb R_+^m}\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
%	\prod_{J}p_J^{\alpha' S_J}.
%\]

The polytope ${\cal P}$ is bounded by inequalities $W_a^JS_J\geq 0$ in the space of $\mathbf X$, where $W_a^J$ is determined by the facet $F_a$ of $\mathcal P$.  These inequalities also cut out a polyhedron in the $(d+m)$-dimensional space of $\mathbf S$, which is defined to be the big polyhedron of $\mathcal P$, 
and the integral $\mathcal I(\mathbf S)$ converges for each point $\mathbf S$ 
inside this polyhedron. Dually, we can describe the big polyhedron by its vertices. Suppose 
$\{V_J^\alpha\}_{1\leq \alpha \leq v}$ are its non-zero vertices ($v$ denotes the number of vertices), a point $\mathbf S$ inside 
the polyhedron can be written as $S_J = F_\alpha V^\alpha_J$ with non-negative coefficients 
$\{F_\alpha\}_{1\leq \alpha \leq v}$.  Therefore, the integral $\mathcal I(\mathbf S)$
can be seen as a function of ``dual coordinates'' $\{F_\alpha\}$ which encourages us to 
rewrite the integral to make it manifest by (here we collectively denote $p_J=(x_1, \cdots, x_d, p_1, \cdots, p_m)$)~\footnote{Note that one can indeed treat the monomials $x_i^{\alpha' X_i}$ on the equal footing as polynomials, since Minkowski sum w.r.t. them amounts to merely translating the polytope $c_I N[p_I]$ by $-X_i$ in the $i$-th direction~\cite{}.}.

\begin{equation}
	\mathcal I(\mathbf F)=
	\int_{\mathbb R_+^d} \prod_{i=1}^d \frac{d x_i}{x_i}~%\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
	\prod_{\alpha}u_\alpha^{\alpha' F_\alpha}
	=
	\int_{\mathbb R_+^d}\prod_{i=1}^d \frac{d x_i}{x_i}~%\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
	\prod_{J}^{d{+}m} p_J^{\alpha' S_J},
\end{equation}
where we introduce a new set of variables $u_\alpha = \prod_J p_J^{V_J^\alpha}$ for 
$\alpha=1,\dots, v$. Note that there's no unique way to write $S_J=F_\alpha V_J^\alpha$ if the big polyhedron is not a simplex, \textit{i.e.} $v>d+m$, and in this case,
$u$-variables $\{u_\alpha \}$ are not independent. Therefore, it is an important special case when the big polyhedron is a simplex, \textit{i.e.} $N=v=d+m$, where $N$ is 
the number of facets of the big polyhedron or the original polytope $\mathcal P$,
and inequalities $F_\alpha=S_J(V^{-1})^J_\alpha \geq 0$ are exactly the inequalities $W_a^J S_J\geq 0$ up to resales $F_\alpha \mapsto t F_\alpha$ for non-zero factors $t$, because
there's no nontrivial linear isometry from the simplex to itself besides permutations of vertices. Therefore, we identity the label of facets $a$ with the label of 
vertices $A$ and get $V=W^{-1}$. Furthermore, every facet of the original polytope $\mathcal P$ can be associated with a single $u_\alpha$ going to zero. 
%Generally, the big polyhedron of a stringy integral is not necessary to be a simplex.

\paragraph{Cluster stringy integrals and binary geometries} A class of very special integrals belong to this case~\cite{}: stringy canonical forms for generalized associahedra of finite-type cluster algebras, namely $A_n$, $B_n$, $C_n$, $D_n$, and exceptional cases ($E_6$, $E_7$, $E_8$, $F_4$, $G_2$). These ``cluster stringy integrals"~\cite{}, and the associated ``cluster configuration space"~\cite{}, turn out to be much more special and rigid extensions of string amplitudes \eqref{stringint} and the moduli space ${\cal M}_{0,n}$, which correspond to the case of type $A_{n{-}3}$. The leading order of such an integral is given by canonical function of the corresponding generalized associahedra, whose combinatorics is attached to the Dynkin diagram (each facet is given by removing a node), {\it e.g.} $D_n \to D_m \times A_{n{-}1{-}m}$ or $A_{n{-}1}$~\cite{}. Even at finite $\alpha'$, it has the remarkable factorization property tied to the Dynkin diagram. Moreover, for type $B/C$ (known as ``cyclohedron") and $D$, the leading order is associated with one-loop bi-adjoint $\phi^3$ amplitudes.

These nice properties become manifest in the configuration space: not only the big polyhedron is a simplex, the $u$-equations are of very special form:
\begin{equation}\label{perfectu}
	1-u_\alpha=\prod_{\beta} u_\beta^{(\beta|\alpha)},
\end{equation}
where the product is over all $N$ variables ($N$ facets), and the integer $(\beta | \alpha)\geq 0$ is the so-called compatibility degree defined in the corresponding cluster algebra~\cite{}.
%Varieties defined by $u$-equations associated with finite type clusters  are called cluster configuration spaces. 
We see that when $u_\alpha$ (for a facet $\alpha$) goes to $0$, it forces all the $u_\beta$ with $\beta | \alpha>0$ goes to $1$ (for facets $\beta$ are exactly those {\it incompatible} with $\alpha$); the remaining $u$'s that are compatible with $u_\alpha$ satisfy $u$ equations for the facet, which factorizes as removing a node of the Dynkin diagram. Therefore, we say that the configuration space is a {\it binary geometry}. Note that this is true also for the complex case, and if we further require all $u$ variables to be positive, we have $0<u<1$ which gives the positive configuration space~\cite{}. The binary property is what guarantees the stringy integral to factorize even at finite $\alpha'$: on the pole $X_\alpha \to 0$, $u_\alpha\to 0$ forces all incompatible $u_\beta\to 1$ which decoupled from $\prod u^{\alpha' X}$, and the integral becomes the factorized one for the facet $\alpha$.

For example, the string integral \eqref{stringint} corresponds to type $A_{n{-}3}$, %and we can use a positive parametrization $z_i=1+x_2+\cdots+x_{i{-}1}$ for $i=2,3,\cdots, n{-}1$ (with gauge fixing $z_1=0, z_2=1$ and $z_n=\infty$). The integral is rewritten as
%\[
%    \mathcal I_n=\int_{\mathbb R_+^{n-3}}
%	\frac{\mathrm dx_2\cdots \mathrm dx_{n-2}}{x_2\cdots x_{n-2}}
%	\prod_{i<j} p_{ij}^{\alpha' s_{ij}},
%\] where $p_{ij}=x_i+\cdots+x_{j-1}$. 
and the $N=n(n{-}3)/2$ $u$ variables of this configuration space are~\cite{}
\[
	u_{i j}=\frac{(z_{i-1}-z_j)(z_i-z_{j-1})}{(z_i-z_j)(z_{i-1}-z_{j-1})},
\]
and they satisfy the $u$-equations
\[
	1-u_{ij}=\prod_{(k,l)\not\sim (i,j)}u_{kl},
\]
where $(i,j)\not\sim (k,l)$ means that the diagonals $(i,j)$ and $(k,l)$ of $n$-gon are crossed, thus the two facets are incompatible (note here compatibility degree is just $0$ or $1$).  For $u_{i,j}\to 0$, all incompatible $u_{k,l} \to 1$, and the remaining $u$'s fall into those of the two polygons divided by $(i,j)$, with their own $u$ equations. The Koba-Nilesen factor becomes $\prod_{i,j} u_{i,j}^{\alpha' X_{i,j}}$ where $X_{i,j}$ are planar variables for the facets of ABHY associahedron, which makes the factorization of string amplitude at finite $\alpha'$ manifest. All these generalize to integrals and configuration spaces for finite type cluster algebra.

@@

%{\bf review of stringy canonical forms, mention big polytopes and $u$ variables in general; then specify to cluster string integrals, then cluster configuration spaces with perfect $u$ equations, do $A_n$, $B_n$ examples; define "binary geometries"}

@@

%Many remarkable aspects of string integral, \textit{e.g.} field-theory limit, 
%factorization, scattering equations, $u$-variables ..., can be carried to
%stringy canonical forms. Almost all of these aspects are related to a hidden 
%polytope $\mathcal P=\sum_I c_I N[p_I]$ of string canonical form 
%eq.\eqref{stringycanonicalform}, where $N[p_I]$ is the Newton polytope of $p_I$ and 
%the sum is understood as the Minkowski sum. For example, 
%eq.\eqref{stringycanonicalform} is convergent if and only if 
%$\mathbf X=(X_1,\dots,X_D)$ is in the interior of $\mathcal P$, equations of
%facets of $\mathcal P$ are massless poles of eq.\eqref{stringycanonicalform}
%and the residue on this facet is still a stringy canonical form of this facet.
%For stringy integrals eq.\eqref{stringint}, these polytopes are nothing but the ABHY
%associahedra~\cite{}.
%
%This polytope can also be realized in $\mathbf x$-space and understood
%as a blow-up of $\mathbb R_+^D$, but it's usually difficult to use $\mathbf x$ to
%describe this polytope, even for the string integrals eq.\eqref{stringint}. For
%example, a facet may correspond to a complicated limit process of $\mathbf x\to 0$
%or $\infty$.
%However, as proven in \cite{},
%the saddle point equations of the Kobe-Nieson factor, \textit{i.e} scattering equations,
%\[
	%\frac{\partial}{\partial x_i}\left(
	%\prod_{i=1}^d x_i^{\alpha'X_i} \prod_I p_I(x)^{-\alpha' c_I},
	%\right)=0\quad \text{for all $i$}
%\]
%give us a diffeomorphism between the interiors of two polytopes in different spaces.

>>>>

{\Large \bf Stringy canonical forms and binary geometries from associahedra, cyclohedra and generalized permutohedra}

@@

Stringy canonical forms are a class of integrals that provide $\alpha'$-deformations of the canonical form of any polytopes. For generalized associahedra of finite-type cluster algebra, there exist completely rigid stringy integrals, whose configuration spaces are the so-called binary geometries, and for classical types are associated with (generalized) scattering of particles and strings. In this paper we propose a large class of rigid stringy canonical forms for another class of polytopes, generalized permutohedra, which also include associahedra and cyclohedra as special cases (type $A_n$ and $B_n$ generalized associahedra). Remarkably, we find that the configuration spaces of such integrals are also binary geometries, which were suspected to exist for generalized associahedra only. For any generalized permutohedron that can be written as Minkowski sum of coordinate simplices, we show that its rigid stringy integral factorizes into products of lower integrals for massless poles at finite $\alpha'$, and the configuration space is binary although the $u$ equations take a more general form than those ``perfect'' ones for cluster cases. Moreover, we provide an infinite class of examples obtained by degenerations of type $A_n$ and $B_n$ integrals, which have perfect $u$ equations as well. Our results provide yet another family of generalizations of the usual string integral and moduli space, whose physical interpretations remain to be explored.

@@

\section{Introduction}
In \cite{Arkani-Hamed:2019mrd} the notion of {\it stringy canonical forms} was introduced which provides vast generalizations of tree-level string amplitudes as integrals over the moduli space ${\cal M}_{0, n}$~\footnote{The study of these types of integrals perhaps dates back to Euler, and more recently they are studied in various contexts, see~\cite{Mellin, Eulermellin, Panzer:2019yxl}. }. Various nice properties of string amplitudes and their field-theory limits, such as factorizations for $\alpha' \to 0$ limit and finite $\alpha'$, channel duality and exponential softness at UV, scattering equations, {\it etc.} all naturally extend to stringy canonical forms. To briefly summarize the idea, let's begin with the disk integral for the open-string amplitudes with ordering $(1,2,\dots, n)$:
\begin{equation}\label{stringint}
{\cal I}^{\rm open-string}_{1,2,\dots,n} (\{s\}):=\int_{\mathcal M_{0,n}^+}
\frac{\mathrm d^{n}z}{\mathrm{SL}(2,\mathbb{R})} \prod_{i=1}^{n}\frac{1}{z_{i}-z_{i{+}1}}
\prod_{i<j}(z_j{-}z_i)^{\alpha' s_{ij}},
\end{equation}
where $\mathcal M_{0,n}^+$ is the positive part of moduli space for the ordering, and $\mathsf{PT}_n:=\frac{\mathrm d^{n}z}{\mathrm{SL}(2,\mathbb{R})} \prod_{i=1}^{n}\frac{1}{z_{i}-z_{i+1}}$ its canonical form~\cite{Arkani-Hamed:2017mur}.  %each factor  $(z_j-z_i)$ in the Kobe-Nieson factor $\prod_{i<j}(z_j-z_i)^{\alpha' s_{ij}}$ is a nowhere vanishing function on $\mathcal M_{0,n}^+$.
With a positive parametrization $\{x_1,\dots,x_{n-3}\}$ of $\mathcal M_{0,n}^+$, 
this canonical form becomes $\prod_{i=1}^{n-3}\mathrm d \log x_i$, and the Koba-Nielsen factor $\prod_{i<j}(z_j-z_i)^{\alpha' s_{i j}}$ becomes a product of powers of polynomials with 
non-negative coefficients~\cite{Arkani-Hamed:2019mrd}: $\prod_i x_i^{\alpha' X_i} \prod_I p_I(x)^{-\alpha' c_I}$. Note that we have factored out $n{-}3$ monomials, $x_i$, and left with $n(n{-}3)/2-(n{-}3)$ positive polynomials $p_I(x)$, with exponents $X_i$'s and $c_I$'s given by linear combinations of the Mandelstam variables $s_{i,j}$.

\paragraph{Stringy canonical forms} Motivated by this rewriting of string integral~\eqref{stringint}, we define a general stringy integral as a $d$-dimensional integral~\cite{Arkani-Hamed:2019mrd}
\begin{equation}\label{stringycanonicalform}
	\mathcal I (\mathbf X,\{c\})=
	\int_{\mathbb R_+^d}\prod_{i=1}^d \frac{\mathrm d x_i}{x_i}x_i^{\alpha'X_i}
	\prod_{I=1}^m p_I(x)^{-\alpha' c_I},
\end{equation}
where we allow $m$ arbitrary Laurent polynomials with non-negative coefficients, $p_I(x)$, and without loss of generality we assume exponents $X_i>0$ and $c_I>0$~\footnote{These are ``positive'' stringy canonical forms, which are integrals over $\mathbb R_+^d$. We can also consider ``complex'' cases with the integrand mod-squared and integrated over $\mathbb C^d$, which are generalizations of closed-string amplitudes~\cite{Arkani-Hamed:2019mrd}.}.

Any integral of the form \eqref{stringycanonicalform} inherits various remarkable properties of string amplitudes \eqref{stringint}, which all depends on the existence of a polytope $\mathcal P:=\sum_I c_I N[p_I]$; here $N[p_I]$ is the Newton polytope of the polynomial $p_I$, and we take the (weighted) Minkowski sum~\cite{Arkani-Hamed:2019mrd}. First of all, one can show that the integral \eqref{stringycanonicalform} is convergent if and only if $\mathbf X=(X_1,\dots,X_d)$ is in the interior of the polytope $\mathcal P$ (we assume that ${\cal P}$ is $d$ dimensional). The leading order of the integral in its $\alpha'$ expansion, dressed with $d^d \mathbf X$, is given by the canonical form of the polytope, ${\Omega}(\cal P)$, thus it can be viewed as an $\alpha'$-deformation of $\Omega(\cal P)$ (hence the name ``stringy canonical form''). Generically the poles of $\Omega(\cal P)$ are given by equations of
facets for $\mathcal P$, which are also poles of the integral at finite $\alpha'$, and the residue on any such pole is given by a stringy canonical form defined for that facet (see~\cite{Arkani-Hamed:2019mrd} for details).

For the string integral \eqref{stringint}, ${\cal P}$ is nothing but the ABHY associahedron~\cite{Arkani-Hamed:2017mur}, whose canonical form gives bi-adjoint $\phi^3$ amplitude as the $\alpha'\to 0$ limit of \eqref{stringint}~\cite{Cachazo:2013iea}. The poles are the planar variables $X_{i,j}$, on which \eqref{stringint} factorizes into lower-point integrals even for finite $\alpha'$. Moreover, the saddle point equations as $\alpha' \to \infty$ can be written as $X_i=\sum_I c_I \partial \log p_I/\partial \log x_i$ for $i=1,\dots, d$; they provide a diffeomorphism from the integration domain to ${\cal P}$, thus $\Omega(\mathcal P)$ can be computed as a pushforward of $\prod_i d\log x_i$ via summing over the saddle points~\cite{Arkani-Hamed:2017tmz}. In particular, for the string integral \eqref{stringint}, the scattering equations provide a map from ${\cal M}_{0,n}^+$ to ABHY associahedron, and the pushforward is equivalent to the CHY formula for $\phi^3$ amplitude~\cite{Cachazo:2013hca,Cachazo:2013iea}.

\paragraph{Configuration spaces} One way to describe the combinatorics of the polytope ${\cal P}$ is through the {\it configuration space}, {\it e.g.} as the blow-up of $\mathbb R_+^D$ in the $\mathbf x$-space. However, it is usually difficult to use $\mathbf x$ for this, even for the string integrals \eqref{stringint}. For example, a facet usually corresponds to a complicated limit process with $x \to 0$ or $\infty$. As proposed in~\cite{Arkani-Hamed:2019plo}, an elegant way to realize ${\cal P}$ in configuration space is by introducing a set of constrained $u$ variables $\{u_\alpha\}$. The configuration space is the variety defined by a set of polynomial equations satisfied by $\{u_\alpha\}$ (or $u$ equations), and the polytope ${\cal P}$ can be realized combinatorially by $\{u_\alpha \geq 0\}$. 
%facet is simply given by an equation $u_A=0$. 
To define the $u$ variables, we first construct the so-called \textit{big polyhedron} in the space $\mathbf S:=(X_1,\dots,X_d,-c_1,\dots,-c_m) \in \mathbb R^{d{+}m}$.  %then $\{u_A\}$ 
%\[
%	\int_{\mathbb R_+^m}\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
%	\prod_{A}u_A^{\alpha' U_A}
%	=
%	\int_{\mathbb R_+^m}\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
%	\prod_{J}p_J^{\alpha' S_J}.
%\]

The polytope ${\cal P}$ is bounded by inequalities $W_a^JS_J\geq 0$ in the space of $\mathbf X$, where $W_a^J$ is determined by the facet $F_a$ of $\mathcal P$.  These inequalities also cut out a polyhedron in the $(d+m)$-dimensional space of $\mathbf S$, which is defined to be the big polyhedron of $\mathcal P$, 
and the integral $\mathcal I(\mathbf S)$ converges for each point $\mathbf S$ 
inside this polyhedron. Dually, we can describe the big polyhedron by its vertices. Suppose 
$\{V_J^\alpha\}_{1\leq \alpha \leq v}$ are its non-zero vertices ($v$ denotes the number of vertices), a point $\mathbf S$ inside 
the polyhedron can be written as $S_J = F_\alpha V^\alpha_J$ with non-negative coefficients 
$\{F_\alpha\}_{1\leq \alpha \leq v}$.  Therefore, the integral $\mathcal I(\mathbf S)$
can be seen as a function of ``dual coordinates'' $\{F_\alpha\}$ which encourages us to 
rewrite the integral to make it manifest by (here we collectively denote $p_J=(x_1, \cdots, x_d, p_1, \cdots, p_m)$)~\footnote{Note that one can indeed treat the monomials $x_i^{\alpha' X_i}$ on the equal footing as polynomials, since Minkowski sum w.r.t. them amounts to merely translating the polytope $c_I N[p_I]$ by $-X_i$ in the $i$-th direction~\cite{Arkani-Hamed:2019mrd}.}
\begin{equation}
	\mathcal I(\mathbf F)=
	\int_{\mathbb R_+^d} \prod_{i=1}^d \frac{d x_i}{x_i}~%\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
	\prod_{\alpha}u_\alpha^{\alpha' F_\alpha}
	=
	\int_{\mathbb R_+^d}\prod_{i=1}^d \frac{d x_i}{x_i}~%\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
	\prod_{J}^{d{+}m} p_J^{\alpha' S_J},
\end{equation}
where we introduce a new set of variables $u_\alpha = \prod_J p_J^{V_J^\alpha}$ for 
$\alpha=1,\dots, v$. Note that there's no unique way to write $S_J=F_\alpha V_J^\alpha$ if the big polyhedron is not a simplex, \textit{i.e.} $v>d+m$, and in this case,
$u$ variables $\{u_\alpha \}$ are not independent. Therefore, it is an important special case when the big polyhedron is a simplex, \textit{i.e.} $N=v=d+m$, where $N$ is 
the number of facets of the big polyhedron or the original polytope $\mathcal P$,
and inequalities $F_\alpha=S_J(V^{-1})^J_\alpha \geq 0$ are exactly the inequalities $W_a^J S_J\geq 0$ up to resales $F_\alpha \mapsto t F_\alpha$ for non-zero factors $t$, because
there's no nontrivial linear isometry from the simplex to itself besides permutations of vertices. Therefore, we identity the label of facets $\alpha$ with the label of 
vertices $J$ and get $V=W^{-1}$. Furthermore, every facet of the original polytope $\mathcal P$ can be associated with a single $u_\alpha$ going to zero. 
%Generally, the big polyhedron of a stringy integral is not necessary to be a simplex.

\paragraph{Cluster stringy integrals and binary geometries} A class of very special integrals belong to this case~\cite{Arkani-Hamed:2019plo}: stringy canonical forms for generalized associahedra of finite-type cluster algebras, namely $A_n$, $B_n$, $C_n$, $D_n$, and exceptional cases ($E_6$, $E_7$, $E_8$, $F_4$, $G_2$). These ``cluster string integrals''~\cite{Arkani-Hamed:2019plo}, and the associated ``cluster configuration spaces''~\cite{Arkani-Hamed:2019plo,Arkani-Hamed:tobeappear}, turn out to be much more special and rigid extensions of string amplitudes \eqref{stringint} and the moduli space ${\cal M}_{0,n}$, which correspond to the case of type $A_{n{-}3}$. The leading order of such an integral is given by canonical function of the corresponding generalized associahedra, whose combinatorics is attached to the Dynkin diagram (each facet is given by removing a node), {\it e.g.} $D_n \to D_m \times A_{n{-}1{-}m}$ or $A_{n{-}1}$~\cite{Arkani-Hamed:2019plo}. Even at finite $\alpha'$, it has the remarkable factorization property tied to the Dynkin diagram. Moreover, for type $B/C$ (known as ``cyclohedron'') and $D$, the leading orders are associated with tadpole emission and one-loop bi-adjoint $\phi^3$ amplitudes, respectively.

These nice properties become manifest in the configuration space: not only the big polyhedron is a simplex, the $u$ equations are of very special form:
\begin{equation}\label{perfectu}
	1-u_\alpha=\prod_{\beta} u_\beta^{(\beta||\alpha)},
\end{equation}
where the product is over all $N$ variables ($N$ facets), and the integer $(\beta || \alpha)\geq 0$ is the so-called compatibility degree defined in the corresponding cluster algebra~\cite{Zelevinskysys}. Varieties defined by $u$ equations associated with finite type clusters  are called cluster configuration spaces.
We see that when $u_\alpha$ (for a facet $\alpha$) goes to $0$, it forces all the $u_\beta$ with $\beta || \alpha>0$ goes to $1$ (for facets $\beta$ are exactly those {\it incompatible} with $\alpha$); the remaining $u$'s that are compatible with $u_\alpha$ satisfy $u$ equations for the facet, which factorizes as removing a node of the Dynkin diagram. Therefore, we say that the configuration space is a {\it binary geometry}. Note that this is true also for the complex case, and if we further require all $u$ variables to be positive, we have $0<u<1$ which gives the positive configuration space~\cite{Arkani-Hamed:2020cig}. The binary property is what guarantees the stringy integral to factorize even at finite $\alpha'$: on the pole $X_\alpha \to 0$, $u_\alpha\to 0$ forces all incompatible $u_\beta\to 1$ which decoupled from $\prod u^{\alpha' X}$, and the integral becomes the factorized one for the facet $\alpha$.

For example, the string integral \eqref{stringint} corresponds to type $A_{n{-}3}$, %and we can use a positive parametrization $z_i=1+x_2+\cdots+x_{i{-}1}$ for $i=2,3,\cdots, n{-}1$ (with gauge fixing $z_1=0, z_2=1$ and $z_n=\infty$). The integral is rewritten as
%\[
%    \mathcal I_n=\int_{\mathbb R_+^{n-3}}
%	\frac{\mathrm dx_2\cdots \mathrm dx_{n-2}}{x_2\cdots x_{n-2}}
%	\prod_{i<j} p_{ij}^{\alpha' s_{ij}},
%\] where $p_{ij}=x_i+\cdots+x_{j-1}$. 
and the $N=n(n{-}3)/2$ $u$ variables of this configuration space are~\cite{Arkani-Hamed:2020cig}
\[
	u_{i j}=\frac{(z_{i-1}-z_j)(z_i-z_{j-1})}{(z_i-z_j)(z_{i-1}-z_{j-1})},
\]
and they satisfy the $u$ equations (see {\it e.g.}~\cite{Brown:2009qja})
\begin{equation}\label{Aueq}
	1-u_{ij}=\prod_{(k,l)\not\sim (i,j)} u_{kl},
\end{equation}
where $(i,j)\not\sim (k,l)$ means that the diagonals $(i,j)$ and $(k,l)$ of $n$-gon are crossed, thus the two facets are incompatible (note here compatibility degree is just $0$ or $1$).  For $u_{i,j}\to 0$, all incompatible $u_{k,l} \to 1$, and the remaining $u$'s fall into those of the two polygons divided by $(i,j)$, with their own $u$ equations. The Koba-Nielsen factor becomes $\prod_{i,j} u_{i,j}^{\alpha' X_{i,j}}$ where $X_{i,j}$ are planar variables for the facets of ABHY associahedron, which makes the factorization of string amplitude at finite $\alpha'$ manifest. All these generalize to integrals and configuration spaces for finite type cluster algebras.

@@

%{\bf review of stringy canonical forms, mention big polytopes and $u$ variables in general; then specify to cluster string integrals, then cluster configuration spaces with perfect $u$ equations, do $A_n$, $B_n$ examples; define ''binary geometries''}

@@

%Many remarkable aspects of string integral, \textit{e.g.} field-theory limit, 
%factorization, scattering equations, $u$ variables ..., can be carried to
%stringy canonical forms. Almost all of these aspects are related to a hidden 
%polytope $\mathcal P=\sum_I c_I N[p_I]$ of string canonical form 
%eq.\eqref{stringycanonicalform}, where $N[p_I]$ is the Newton polytope of $p_I$ and 
%the sum is understood as the Minkowski sum. For example, 
%eq.\eqref{stringycanonicalform} is convergent if and only if 
%$\mathbf X=(X_1,\dots,X_D)$ is in the interior of $\mathcal P$, equations of
%facets of $\mathcal P$ are massless poles of eq.\eqref{stringycanonicalform}
%and the residue on this facet is still a stringy canonical form of this facet.
%For stringy integrals eq.\eqref{stringint}, these polytopes are nothing but the ABHY
%associahedra~\cite{}.
%
%This polytope can also be realized in $\mathbf x$-space and understood
%as a blow-up of $\mathbb R_+^D$, but it's usually difficult to use $\mathbf x$ to
%describe this polytope, even for the string integrals eq.\eqref{stringint}. For
%example, a facet may correspond to a complicated limit process of $\mathbf x\to 0$
%or $\infty$.
%However, as proven in \cite{},
%the saddle point equations of the Kobe-Nieson factor, \textit{i.e} scattering equations,
%\[
	%\frac{\partial}{\partial x_i}\left(
	%\prod_{i=1}^d x_i^{\alpha'X_i} \prod_I p_I(x)^{-\alpha' c_I},
	%\right)=0\quad \text{for all $i$}
%\]
%give us a diffeomorphism between the interiors of two polytopes in different spaces.
